\huspacy: an industrial-strength Hungarian natural language processing toolkit

### 2022-01-04 mszny2022/main.tex
Added authors and page numbers

%\pagestyle{myheadings}
%\def\leftmark{{\rm XIV. Magyar Sz\'am\'\i t\'og\'epes Nyelv\'eszeti Konferencia}}
%\def\rightmark{{\rm Szeged, 2018. január 18-19.}}

%  \setcounter{page}{1}

\title{\huspacy: an industrial-strength Hungarian natural language processing toolkit}
%a november 15-ig bekuldott verziobol kerjuk a szerzok adatait kihagyni
%	\author{Orosz György\inst{1}, Farkas Richárd\inst{1}, Vincze Veronika\inst{1,2}\\
% \institute{$^1$Szegedi Tudom\'anyegyetem, Informatikai Int\'ezet\break
%Szeged, \'Arp\'ad t\'er 2.\break
%$^2$MTA-SZTE Mesters\'eges Intelligencia Kutat\'ocsoport\break
%Szeged, Tisza Lajos k\"or\'ut 103.\break 
%\{zsibrita,rfarkas,vinczev\}@inf.u-szeged.hu\break
%}
%}

@@

We present \huspacy{}, a new industry-ready Hungarian natural language processing toolkit\footnote{We implemented our pipeline in spaCy v3.x. Prior to this work, there were attempts (\url{https://github.com/oroszgy/spacy-hungarian-models}) to support Hungarian in this framework, but none of those releases are compatible with the tool’s current version.}. 
It provides all the aforementioned basic text processing modules with high accuracy. The underlying models are optimized to be light on memory consumption and CPU usage. The presented tool is open source\footnote{The URL is to be shared in the final paper.} and is available under the permissive CC-BY-SA-4.0 license. Our system is built on top of spaCy’s infrastructure, thus extensive documentation, debugging tools, an ergonomic API and a flourishing ecosystem are already provided.

@@

\newlength{\llem}
\settowidth{\llem}{Accuracy}
\begin{table}
\begin{center}
\begin{tabular}{
    l<{\hspace{1em}}
  >{\centering\arraybackslash}m{\llem}
}
\toprule
              & Accuracy \\
\midrule
\stanza{}        & 94.25\%    \\
\udpipe{}        & 88.50\%    \\
\udpipe{}         & 94.94\%    \\
\huspacy{} (UD)  & 94.82\%    \\
\huspacy{} (SZC) & 95.43\%    \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Lemmatization accuracy of NLP pipelines measured on the test set of the Hungarian UD Corpus. \huspacy{} (UD) uses the same setting as its contenders, while \huspacy{} (SZC) uses the whole Szeged Corpus (except the sentences of the test set) for training.}
\label{table:lemma}
\end{center}
\end{table}

>>>>

\pagestyle{myheadings}
\def\leftmark{{\rm XVIII. Magyar Sz\'am\'\i t\'og\'epes Nyelv\'eszeti Konferencia}}
\def\rightmark{{\rm Szeged, 2022. január 27-28.}}

% \setcounter{page}{1}
% \pagestyle{plain}

\title{\huspacy: an industrial-strength Hungarian natural language processing toolkit}

\author{György Orosz\inst{1,2} \and
    Zsolt Szántó\inst{1,2} \and \break
    Péter Berkecz\inst{1,2} \and
    Gergő Szabó\inst{1,2} \and
    Farkas Richárd\inst{1,2}\\
    \institute{
        $^1$Artificial Intelligence National Laboratory \break
        $^2$Institute of Informatics, University of Szeged\break
        Szeged Árpád tér 2., H-6720
    }
    \email{gyorgy@orosz.link}\break
    \email{\{szantozs,rfarkas\}@inf.u-szeged.hu}\break
    \email{\{berkecz.peter,szabogergo.a\}@gmail.com}\break
}

@@

We present \huspacy{}, a new industry-ready Hungarian natural language processing toolkit\footnote{We implemented our pipeline in spaCy v3.x. Prior to this work, there were attempts (\url{https://github.com/oroszgy/spacy-hungarian-models}) to support Hungarian in this framework, but none of those releases are compatible with the tool’s current version.}. 
It provides all the aforementioned basic text processing modules with high accuracy. The underlying models are optimized to be light on memory consumption and CPU usage. The presented tool is open source\footnote{\url{https://github.com/oroszgy/spacy-hungarian-models}} and is available under the permissive CC-BY-SA-4.0 license. Our system is built on top of spaCy’s infrastructure, thus extensive documentation, debugging tools, an ergonomic API and a flourishing ecosystem are already provided.

@@

\newlength{\llem}
\settowidth{\llem}{Accuracy}
\begin{table}
\begin{center}
\begin{tabular}{
    l<{\hspace{1em}}
  >{\centering\arraybackslash}m{\llem}
}
\toprule
              & Accuracy \\
\midrule
\stanza{}        & 94.25\%    \\
\udpipe{} v1     & 88.50\%    \\
\emtsv{}         & 94.94\%    \\
\huspacy{} (UD)  & 94.82\%    \\
\huspacy{} (SZC) & 95.43\%    \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Lemmatization accuracy of NLP pipelines measured on the test set of the Hungarian UD Corpus. \huspacy{} (UD) uses the same setting as its contenders, while \huspacy{} (SZC) uses the whole Szeged Corpus (except the sentences of the test set) for training.}
\label{table:lemma}
\end{center}
\end{table}
